The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-07-01 borel-regularity.tex
Drop unused package
Hide `verify`, `unstable`, `todo`, `old` environments
Correct DLMF citation
Hide draft text and turn off revision highlighting
Change organization from list to paragraphs

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[square,numbers,sort,compress]{natbib}
\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
\usepackage[scr=boondoxo, scrscaled=1.05]{mathalpha} %% hat tip https://tex.stackexchange.com/a/247819
%%\usepackage{bm} %% for putting series names in bold
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[margin=1cm]{caption}
\usepackage{enumitem}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{rotating} % for \isoarrow
\usepackage{environ} % to hide verifications and stuff

@@

% hideable verifications
\newif\ifshowverify
\showverifytrue
\ifshowverify
\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
\else
\NewEnviron{verify}{\iffalse\expandafter\BODY\fi}
\fi

% hideable notes for unstable references
\newif\ifshowunstable
\showunstabletrue
\ifshowunstable
\newenvironment{unstable}{\color{YellowGreen}}{\color{black}}
\else
\NewEnviron{unstable}{\iffalse\expandafter\BODY\fi}
\fi
\newcommand{\citesection}[1]{\begin{unstable}\texttt{#1}\end{unstable}}

% hideable to-do notes and brainstorming
\newif\ifshowtodo
\showtodotrue
\ifshowtodo
\newenvironment{todo}{\color{Coral}}{\color{black}}
\newenvironment{brainstorm}{\color{BlueViolet}\begin{itemize}}{\end{itemize}\color{black}}
\else
\NewEnviron{todo}{\iffalse\expandafter\BODY\fi}
\NewEnviron{brainstorm}{\iffalse\expandafter\BODY\fi}
\fi

% hideable old text
\newif\ifshowold
\showoldtrue
\ifshowold
\newenvironment{old}{\color{RoyalBlue}}{\color{black}}
\else
\NewEnviron{old}{\iffalse\expandafter\BODY\fi}
\fi

% more drafting environments
\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
\newenvironment{revised}{\color{DarkBlue}}{\color{black}}

@@

In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
 \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
\paragraph{Links to resurgence}
The examples we study all involve {\em resurgent functions} in the position domain. \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}. Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}. Conjecturally, this property extends to more general thimble integrals---perhaps even infinite-dimensional ones \cite[examples~5--6]{Maxim_slide_ERC}. The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave. \begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
\subsection{Organization of the paper}\label{sec:org}
\begin{paragraph}{Section~\ref{sec:historical-context}}
We contextualize our work by reviewing some classical results related to Borel regularity. These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.\end{paragraph}
\begin{paragraph}{Section~\ref{sec:Laplace-Borel-general}}
We introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results. To make this section more self-contained, we review basic definitions and properties in Section~\ref{laplace:ordinary} and the beginnings of Sections \ref{sec:geometry_borel} and \ref{sec:borel-laplace-homom}.
\end{paragraph}
\begin{paragraph}{Section~\ref{sec:proof_main_results}}
We restate and prove our main results.
\end{paragraph}
\begin{paragraph}{Section~\ref{sec:examples}}
We illustrate our results by working through detailed examples of how Borel regular functions arise, both as $1$-dimensional thimble integrals and as solutions of level~$1$ ODEs.
\end{paragraph}
\begin{paragraph}{Appendix~\ref{airy-appendix}}
Reprising our analysis of the Airy--Lucas equations in Section~\ref{sec:examples}, we focus on the Airy equation as a concrete special case. We then explain how our treatment lines up with other discussions of the Airy equation in the literature on Borel summation.
\end{paragraph}
\begin{paragraph}{Appendix~\ref{shifting}}
We prove a fact about the relationship between integral and differential equations which is used in some of our examples.
\end{paragraph}
\begin{todo}\par [Consider going back to non-separated style.]\end{todo}\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles. This could help the reader to contextualize our results in the literature. Then, in Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform. The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{laplace:ordinary}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}. Then, Section~\ref{sec:proof_main_results} contains proofs of the main results. Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one. 
We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject. \begin{todo}[Appendix~\ref{shifting}?]\end{todo}
\end{draft}
\subsection{Notation}
In reasoning about Borel summation, it is important to keep track of whether we are working with holomorphic functions or formal series, and whether we are working on the position domain (the Borel plane) or the frequency domain (the $z$ plane). We have adopted a variable naming convention that makes these distinctions apparent at a glance.
\begin{notation*}
Functions and series on the frequency and position domains are named as follows.
\begin{tabular}{c|c|c}
& \textbf{Analytic}: no tilde & \textbf{Formal}: tilde \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\phi$ & $\series{\phi}$ \\[1mm]
\end{tabular}
We will sometimes use a hat to emphasize that we got a holomorphic function $\hat{\phi}$ by taking the sum of formal series $\series{\phi}$.

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[square,numbers,sort,compress]{natbib}
\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
\usepackage[scr=boondoxo, scrscaled=1.05]{mathalpha} %% hat tip https://tex.stackexchange.com/a/247819
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[margin=1cm]{caption}
\usepackage{enumitem}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{rotating} % for \isoarrow
\usepackage{environ} % to hide verifications and stuff

@@

% hideable verifications
\newif\ifshowverify
\showverifyfalse
\ifshowverify
\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
\else
\NewEnviron{verify}{\iffalse\expandafter\BODY\fi}
\fi

% hideable notes for unstable references
\newif\ifshowunstable
\showunstablefalse
\ifshowunstable
\newenvironment{unstable}{\color{YellowGreen}}{\color{black}}
\else
\NewEnviron{unstable}{\iffalse\expandafter\BODY\fi}
\fi
\newcommand{\citesection}[1]{\begin{unstable}\texttt{#1}\end{unstable}}

% hideable to-do notes and brainstorming
\newif\ifshowtodo
\showtodofalse
\ifshowtodo
\newenvironment{todo}{\color{Coral}}{\color{black}}
\newenvironment{brainstorm}{\color{BlueViolet}\begin{itemize}}{\end{itemize}\color{black}}
\else
\NewEnviron{todo}{\iffalse\expandafter\BODY\fi}
\NewEnviron{brainstorm}{\iffalse\expandafter\BODY\fi}
\fi

% hideable old text
\newif\ifshowold
\showoldfalse
\ifshowold
\newenvironment{old}{\color{RoyalBlue}}{\color{black}}
\else
\NewEnviron{old}{\iffalse\expandafter\BODY\fi}
\fi

% hideable draft text
\newif\ifshowdraft
\showdraftfalse
\ifshowdraft
\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
\else
\NewEnviron{draft}{\iffalse\expandafter\BODY\fi}
\fi

% highlightable revisions
\newif\ifhighlightrevs
\highlightrevsfalse
\ifhighlightrevs
\newenvironment{revised}{\color{DarkBlue}}{\color{black}}
\else
\newenvironment{revised}{}{}
\fi

@@

In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
 \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
%
\paragraph{Links to resurgence}
%
The examples we study all involve {\em resurgent functions} in the position domain. \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}. Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}. Conjecturally, this property extends to more general thimble integrals---perhaps even infinite-dimensional ones \cite[examples~5--6]{Maxim_slide_ERC}. The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave. \begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
%
\subsection{Organization of the paper}\label{sec:org}
%
\begin{revised}
In Section~\ref{sec:historical-context}, we contextualize our work by reviewing some classical results related to Borel regularity. These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.

In section~\ref{sec:Laplace-Borel-general}, we introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results. To make this section more self-contained, we review basic definitions and properties in Section~\ref{laplace:ordinary} and the beginnings of Sections \ref{sec:geometry_borel} and \ref{sec:borel-laplace-homom}.

In Section~\ref{sec:proof_main_results}, we restate and prove our main results. In Section~\ref{sec:examples}, we illustrate our results by working through detailed examples of how Borel regular functions arise, both as $1$-dimensional thimble integrals and as solutions of level~$1$ ODEs.

In Appendix~\ref{airy-appendix}, reprising our analysis of the Airy--Lucas equations in Section~\ref{sec:examples}, we focus on the Airy equation as a concrete special case. We then explain how our treatment lines up with other discussions of the Airy equation in the literature on Borel summation.

In Appendix~\ref{shifting}, we prove a fact about the relationship between integral and differential equations which is used in some of our examples.
\end{revised}
%
\begin{todo}\par [Consider going back to non-separated style.]\end{todo}\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles. This could help the reader to contextualize our results in the literature. Then, in Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform. The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{laplace:ordinary}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}. Then, Section~\ref{sec:proof_main_results} contains proofs of the main results. Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one. 
We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject. \begin{todo}[Appendix~\ref{shifting}?]\end{todo}
\end{draft}
%
\subsection{Notation}
In reasoning about Borel summation, it is important to keep track of whether we are working with holomorphic functions or formal series, and whether we are working on the position domain (the Borel plane) or the frequency domain (the $z$ plane). We have adopted a variable naming convention that makes these distinctions apparent at a glance.
\begin{notation*}
Functions and series on the frequency and position domains are named as follows.
\begin{center}
\begin{tabular}{c|c|c}
& \textbf{Analytic}: no tilde & \textbf{Formal}: tilde \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\phi$ & $\series{\phi}$ \\[1mm]
\end{tabular}
\end{center}
We will sometimes use a hat to emphasize that we got a holomorphic function $\hat{\phi}$ by taking the sum of formal series $\series{\phi}$.
